### 2018-03-15 submission/manuscript.Rmd
update order of supplemental figs

**Figure S2: Relative importance of taxa (A) and OTUs (B) in Random Forest models for differentiating between individuals with normal colons and carcinomas using stool samples.** These taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure S3: Relative importance of taxa (A, B) and OTUs (C, D) in Random Forest models for differentiating between individuals with normal colons and carcinomas using matched (A, C) and unmatched (B, D) tissue samples.** hese taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure S4: Comparison of Random Forest modeling approaches to classify individuals as having normal colons or adenomas (A) or carcinomas (B) when training the models using the taxa with significant ORs, all taxa in a community, or all OTUs in a community when using data from tissue samples.** No taxa had a significant OR associated with the presence of adenomas using tissue samples. The black line represents the median AUC for the respective group. The dashed gray line indicates an AUC of 0.5.

>>>>

**Figure S2: Comparison of Random Forest modeling approaches to classify individuals as having normal colons or adenomas (A) or carcinomas (B) when training the models using the taxa with significant ORs, all taxa in a community, or all OTUs in a community when using data from tissue samples.** No taxa had a significant OR associated with the presence of adenomas using tissue samples. The black line represents the median AUC for the respective group. The dashed gray line indicates an AUC of 0.5.

**Figure S3: Relative importance of taxa (A) and OTUs (B) in Random Forest models for differentiating between individuals with normal colons and carcinomas using stool samples.** These taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

**Figure S4: Relative importance of taxa (A, B) and OTUs (C, D) in Random Forest models for differentiating between individuals with normal colons and carcinomas using matched (A, C) and unmatched (B, D) tissue samples.** hese taxa and OTUs were among the top 10% most important features in each model. The colors indicate the z-transformed (i.e. mean of 0.0 and standard deviation of 1.0) mean decrease in accuracy values calculated from the model for each study. The taxa are ranked by their mean z-score-transformed mean decrease in accuracy.

### 2018-03-15 submission/manuscript.tex
update order of supplemental figs

\textbf{Figure S2: Relative importance of taxa (A) and OTUs (B) in
Random Forest models for differentiating between individuals with normal
colons and carcinomas using stool samples.} These taxa and OTUs were
among the top 10\% most important features in each model. The colors
indicate the z-transformed (i.e.~mean of 0.0 and standard deviation of
1.0) mean decrease in accuracy values calculated from the model for each
study. The taxa are ranked by their mean z-score-transformed mean
decrease in accuracy.

\textbf{Figure S3: Relative importance of taxa (A, B) and OTUs (C, D) in
Random Forest models for differentiating between individuals with normal
colons and carcinomas using matched (A, C) and unmatched (B, D) tissue
samples.} hese taxa and OTUs were among the top 10\% most important
features in each model. The colors indicate the z-transformed (i.e.~mean
of 0.0 and standard deviation of 1.0) mean decrease in accuracy values
calculated from the model for each study. The taxa are ranked by their
mean z-score-transformed mean decrease in accuracy.

\textbf{Figure S4: Comparison of Random Forest modeling approaches to
classify individuals as having normal colons or adenomas (A) or
carcinomas (B) when training the models using the taxa with significant
ORs, all taxa in a community, or all OTUs in a community when using data
from tissue samples.} No taxa had a significant OR associated with the
presence of adenomas using tissue samples. The black line represents the
median AUC for the respective group. The dashed gray line indicates an
AUC of 0.5.

>>>>

\textbf{Figure S2: Comparison of Random Forest modeling approaches to
classify individuals as having normal colons or adenomas (A) or
carcinomas (B) when training the models using the taxa with significant
ORs, all taxa in a community, or all OTUs in a community when using data
from tissue samples.} No taxa had a significant OR associated with the
presence of adenomas using tissue samples. The black line represents the
median AUC for the respective group. The dashed gray line indicates an
AUC of 0.5.

\textbf{Figure S3: Relative importance of taxa (A) and OTUs (B) in
Random Forest models for differentiating between individuals with normal
colons and carcinomas using stool samples.} These taxa and OTUs were
among the top 10\% most important features in each model. The colors
indicate the z-transformed (i.e.~mean of 0.0 and standard deviation of
1.0) mean decrease in accuracy values calculated from the model for each
study. The taxa are ranked by their mean z-score-transformed mean
decrease in accuracy.

\textbf{Figure S4: Relative importance of taxa (A, B) and OTUs (C, D) in
Random Forest models for differentiating between individuals with normal
colons and carcinomas using matched (A, C) and unmatched (B, D) tissue
samples.} hese taxa and OTUs were among the top 10\% most important
features in each model. The colors indicate the z-transformed (i.e.~mean
of 0.0 and standard deviation of 1.0) mean decrease in accuracy values
calculated from the model for each study. The taxa are ranked by their
mean z-score-transformed mean decrease in accuracy.
